Explicit B-spline regularization in diffeomorphic image registration

### 2013-10-26 paper.tex
ENH:  Jambi

antsRegistration --dimensionality 3 \
                 --output ${prefix} \
                 --use-histogram-matching 1 \
                 --initial-moving-transform [${fixed},${moving},1] \
                 --transform Rigid[0.1] \
                 --metric MI[${fixed},${moving},1,32,Regular,0.25] \ 
                 --convergence 1000x500x250 \
                 --smoothing-sigmas 2.0x1.0x0.0mm \
                 --shrink-factors 4x3x2 \
                 --transform Affine[0.1] \
                 --metric MI[${fixed},${moving},1,32,Regular,0.25] \ 
                 --convergence 1000x500x250 \
                 --smoothing-sigmas 2.0x1.0x0.0mm \
                 --shrink-factors 4x3x2 \
                 --transform BSplineSyN[0.1,26,0x0x0,3] \
                 --metric CC[${fixed},${moving},1,4] \ 
                 --convergence 100x70x50x20 \
                 --smoothing-sigmas 2x1.0x0.5x0.0mm \
                 --shrink-factors 6x4x2x1

>>>>

antsRegistration --dimensionality 3 \
                 --output ${prefix} \
                 --use-histogram-matching 1 \
                 --initial-moving-transform [${fixed},${moving},1] \
                 --transform Rigid[0.1] \
                 --metric MI[${fixed},${moving},1,32,Regular,0.25] \ 
                 --convergence 1000x500x250 \
                 --smoothing-sigmas 2.0x1.0x0.0mm \
                 --shrink-factors 4x3x2 \
                 --transform Affine[0.1] \
                 --metric MI[${fixed},${moving},1,32,Regular,0.25] \ 
                 --convergence 1000x500x250 \
                 --smoothing-sigmas 2.0x1.0x0.0mm \
                 --shrink-factors 4x3x2 \
                 --transform BSplineSyN[0.1,26,0,3] \
                 --metric CC[${fixed},${moving},1,4] \ 
                 --convergence 100x70x50x20 \
                 --smoothing-sigmas 2x1.0x0.5x0.0mm \
                 --shrink-factors 6x4x2x1
